### 2015-04-22 thesis/thesis/chap6/chap6.tex
changes

There is still a long way to go in order to develop a comprehensive framework for probabilistic social commitments in MASs. In the future, we plan to extend our work by investigating several directions.

First, time complexity and space complexity of our proposed verification techniques are not analysed yet. Therefore, we intend to compute the complexity of the proposed reduction techniques of the three components.

Second, we are planning to extend our framework to support more commitment schemes such as many-to-one and many-to-many commitments. This is extremely important because in real settings there exist situations where performing such commitment scenarios contributes towards improving the efficiency of MASs.

Third, integrating more commitment actions (such as assign, delegate, ..etc) \cite{Singh2000} are of a great interest to investigate. This helps ensure that all possible commitment operations employed in probabilistic environments are adequately dealt with.

Forth, we intend to explore the interaction between social commitments and norms in probabilistic systems.

Fifth, another direction that we intend to explore is the probabilistic conditional social commitments. Conditional social commitment is still in  its infancy \cite{Kholy2014} and investigating it in systems exhibiting stochastic behavior is an open point for research.

Finally, we plan to extend the PRISM model checker to accommodate our new operators (i.e. commitment and group commitment) and then develop dedicated verification algorithms for the proposed logics and implement them directly into PRISM. So doing will allow us to compare the results obtained from the indirect method (reduction-based techniques) with the results of the direct method (dedicated algorithms).

@@

%. Abstracting tokens and control paths

%This thesis can be extended in the following directions.
% \begin{itemize}
%   \item Extend our semantic to support more SysML features,
%   \item We intend to formalize SysML and UML daigrams such as state machines and sequence diagrams,  then,
%   \item Extend our framework to support them
%   \item Extend the specification framework to handle the reliability requirements and prove formally the soundness of the proposed framework.
%   \item we intend to transform a SysML activity diagram to its fractal form in order to benefit from our abstraction framework. This helps in the abstraction/refinement process of UML/SysML diagrams. Second, we extend our framework to handle other UML and SysML models such as state machine and sequence diagrams.
%  \item  Finally, we intend to investigate reducing the property within the model and applying our approach on different real systems.
%  \item Abstracting tokens and control paths.
%  \item Framework Extension: Extend our security verification framework to support other SysML behavioral diagrams: State machine, and Sequence diagrams,
%  \item Ensure the equivalence between SysML behavioral diagrams,
%  \item Extract the syntax from the metamodels.
%  \item Studying the completeness of system completeness.
%  \item Compositional verification for other operators.
%  \item we plan to extend our framework to handle more compositional verification techniques like assume-guaranty.
%  \item we explore other abstraction approaches especially data abstraction targeting more system features like time and data.
%  \item Finally, we intend to investigate reducing the property within the model.
%   \item Finally, we want to validate our approach on cyber-forensics systems.
% \end{itemize}

%In future, we would like to extend our work by investigating several directions.
%First, we intend to build our implementation within PRISM model checker. Second, we plan to extend our framework to handle more compositional verification techniques like assume-guaranty. Next, we explore other abstraction approaches especially data abstraction targeting more system features like time and data.

>>>>

There is

@@
